### 2013-12-29 image_proc_methods.tex
new ROI figure and associated text

The 3D models were used to render volume estimates of the PZ and CG, with the
sum of PZ and CG representing the total prostate gland volume. AFS volume
estimates in select MR cases were included in the total prostate gland volume
estimates. Orthogonal tri-axial measurements in the lateral-to-lateral,
apex-to-base, and anterior-to-posterior dimensions were made in slicer by
placing an ROI cube in the model's center and expanding the ROI cube to fit the
maximal model dimensions.

>>>>

The 3D models were used to render volume estimates of the PZ and CG, with the
sum of PZ and CG representing the total prostate gland volume. AFS volume
estimates in select MR cases were included in the total prostate gland volume
estimates. Orthogonal tri-axial measurements in the lateral-to-lateral,
apex-to-base, and anterior-to-posterior dimensions were made in slicer by
placing an ROI cube in the model's center and expanding the ROI cube to fit the
maximal model dimensions (Figure~\ref{fig:roi_tool}).
